Measuring Individual Partisan Harm in Redistricting

### 2021-09-12 paper/paper.Rmd
NJ

>>>>

```{r nj-district-shares, fig.cap="Distribution of district vote shares, with districts ordrered by Democratic two-part vote share, and divided by quantile for each of three districting measures.", fig.width=6.5, fig.height=4.875}
include_graphics(here("paper/figures/nj_district_shares.pdf"))
```

This is manifested in the district-level vote shares shown in Figure \ref{fig:nj-district-shares}.
Within each districting plan, we number districts in order of their Democratic vote share, with district 1 the least Democratic.
The figure shows the distribution of these vote shares for each ordered district, but broken out according to each plan's values of $F(q)$, $U^{(G)}$, and $U^{(L)}$.
